Gaps in stellar streams as a result of globular cluster fly-bys

### 2025-01-13 paper/main.tex
full compilation
updated the caption for tail coordinates

  \section{Gap Detection} \label{sec:gap_detection}
    For each of the 50 simulations, we compare the final snapshots between the \texttt{reference} and \texttt{full} simulations using the tail coordinate system, as shown in Fig.~\ref{fig:TailCoordinates}. The \texttt{reference} simulations were only saved at the final time-stamps, thus from Eq.~\ref{eq:data_volume_estimate} where $N_ts$=1, leading to a data volume of about one hundred measly megabytes. We inspect these differences by generating 2D density maps of the streams. Additionally, we marginalize over the $y'$-coordinate to produce 1D density profiles along the $x'$-axis. These comparisons are shown in the results section (see Fig.~\ref{fig:profiles}).
    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{along_orbit_coordinate_system-approved.png}
      \caption{Tail coordinates. \textbf{I want to update this}. }
      \label{fig:TailCoordinates}
    \end{figure}

>>>>

  \section{Gap Detection} \label{sec:gap_detection}
    For each of the 50 simulations, we compare the final snapshots between the \texttt{reference} and \texttt{full} simulations using the tail coordinate system, as shown in Fig.~\ref{fig:TailCoordinates}. The \texttt{reference} simulations were only saved at the final time-stamps, thus from Eq.~\ref{eq:data_volume_estimate} where $N_ts$=1, leading to a data volume of about one hundred measly megabytes. We inspect these differences by generating 2D density maps of the streams. Additionally, we marginalize over the $y'$-coordinate to produce 1D density profiles along the $x'$-axis. These comparisons are shown in the results section (see Fig.~\ref{fig:profiles}).
    \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{tailcoordinates.png}
      \caption{A demonstration of the transformation from galactic coordinates to tail coordinates. The black dot represents the globular cluster, while the thick black line shows a segment of its orbit. A star particle is marked with a star symbol. The red vector points from the nearest point on the cluster's orbit to the star particle. Its projection onto the galactocentric unit vector is shown in green and labeled $y'$. The red vector is also projected onto the vector perpendicular to both the orbital tangent and the galactocentric vector, which defines the local orbital plane and is labeled $z'$. The path length along the orbit from the cluster to the nearest point is denoted as $x'$, with $x'$ being positive if the particle is ahead of the cluster.}
      \label{fig:TailCoordinates}
    \end{figure}
